### 2021-10-14 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_ncbitaxonomy_softwarenote@6e49d36327da7c3212c875fbbe50627e080e7616 🚀

%!TEX TS-program = xelatex
\documentclass[11pt]{article}

\usepackage[english]{babel}

\usepackage{amsmath,amssymb,amsfonts}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{stix2}
\usepackage[scaled]{helvet}
\usepackage[scaled]{inconsolata}

\usepackage{lastpage}

\usepackage{setspace}

\usepackage{ccicons}

\usepackage[hang,flushmargin]{footmisc}

\usepackage{geometry}

\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}

\usepackage{fancyhdr}
\renewcommand{\headrulewidth}{0pt}\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}

\makeatletter
\newcounter{tableno}
\newenvironment{tablenos:no-prefix-table-caption}{
  \caption@ifcompatibility{}{
    \let\oldthetable\thetable
    \let\oldtheHtable\theHtable
    \renewcommand{\thetable}{tableno:\thetableno}
    \renewcommand{\theHtable}{tableno:\thetableno}
    \stepcounter{tableno}
    \captionsetup{labelformat=empty}
  }
}{
  \caption@ifcompatibility{}{
    \captionsetup{labelformat=default}
    \let\thetable\oldthetable
    \let\theHtable\oldtheHtable
    \addtocounter{table}{-1}
  }
}
\makeatother

\usepackage{array}
\newcommand{\PreserveBackslash}[1]{\let\temp=\\#1\let\\=\temp}
\let\PBS=\PreserveBackslash

\usepackage[breaklinks=true]{hyperref}
\hypersetup{colorlinks,%
citecolor=blue,%
filecolor=blue,%
linkcolor=blue,%
urlcolor=blue}
\usepackage{url}

\usepackage{caption}
\setcounter{secnumdepth}{0}
\usepackage{cleveref}

\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth
\else\Gin@nat@width\fi}
\makeatother
\let\Oldincludegraphics\includegraphics
\renewcommand{\includegraphics}[1]{\Oldincludegraphics[width=\maxwidth]{#1}}

\usepackage{longtable}
\usepackage{booktabs}

\usepackage{color}
\usepackage{fancyvrb}
\newcommand{\VerbBar}{|}
\newcommand{\VERB}{\Verb[commandchars=\\\{\}]}
\DefineVerbatimEnvironment{Highlighting}{Verbatim}{commandchars=\\\{\}}
% Add ',fontsize=\small' for more characters per line
\usepackage{framed}
\definecolor{shadecolor}{RGB}{248,248,248}
\newenvironment{Shaded}{\begin{snugshade}}{\end{snugshade}}
\newcommand{\KeywordTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
\newcommand{\DataTypeTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{#1}}
\newcommand{\DecValTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
\newcommand{\BaseNTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
\newcommand{\FloatTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
\newcommand{\ConstantTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\CharTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\SpecialCharTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\StringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\VerbatimStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\SpecialStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\ImportTok}[1]{#1}
\newcommand{\CommentTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{#1}}}
\newcommand{\DocumentationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\AnnotationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\CommentVarTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\OtherTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{#1}}
\newcommand{\FunctionTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\VariableTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\ControlFlowTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
\newcommand{\OperatorTok}[1]{\textcolor[rgb]{0.81,0.36,0.00}{\textbf{#1}}}
\newcommand{\BuiltInTok}[1]{#1}
\newcommand{\ExtensionTok}[1]{#1}
\newcommand{\PreprocessorTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{#1}}}
\newcommand{\AttributeTok}[1]{\textcolor[rgb]{0.77,0.63,0.00}{#1}}
\newcommand{\RegionMarkerTok}[1]{#1}
\newcommand{\InformationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\WarningTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\AlertTok}[1]{\textcolor[rgb]{0.94,0.16,0.16}{#1}}
\newcommand{\ErrorTok}[1]{\textcolor[rgb]{0.64,0.00,0.00}{\textbf{#1}}}
\newcommand{\NormalTok}[1]{#1}

\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newenvironment{CSLReferences}[3] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1 \everypar{\setlength{\hangindent}{\cslhangindent}}\ignorespaces\fi
  % set entry spacing
  \ifnum #2 > 0
  \setlength{\parskip}{#2\baselineskip}
  \fi
 }%
 {}
\usepackage{calc} % for \widthof, \maxof
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\maxof{\widthof{#1}}{\csllabelwidth}}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth}{#1}}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}\geometry{verbose,letterpaper,tmargin=2.2cm,bmargin=2.2cm,lmargin=2.2cm,rmargin=2.2cm}

\usepackage{lineno}
\usepackage[nolists,noheads]{endfloat}

\pagestyle{plain}

\tolerance=1
\emergencystretch=\maxdimen
\hyphenpenalty=10000
\hbadness=10000

\doublespacing

\fancypagestyle{normal}
{
  \fancyhf{}
  \fancyfoot[R]{\footnotesize\sffamily\thepage\ of \pageref*{LastPage}}
}
\begin{document}
\raggedright
\thispagestyle{empty}
{\Large\bfseries\sffamily Template to prepare preprints and manuscripts
using markdown and github actions}
\vskip 5em

%
\href{https://orcid.org/0000-0002-0735-5184}{Timothée\,Poisot}%
%
\,\textsuperscript{1,2,‡}\quad %
Peregrin\,Took%
%
\,\textsuperscript{3,4}\quad %
Merriadoc\,Brandybuck%
%
\,\textsuperscript{5,4,‡}

\textsuperscript{1}\,Université de
Montréal\quad \textsuperscript{2}\,Québec Centre for Biodiversity
Sciences\quad \textsuperscript{3}\,Inn of the Prancing
Pony\quad \textsuperscript{4}\,Fellowship of the
Ring\quad \textsuperscript{5}\,Green Dragon Inn

\textsuperscript{‡}\,These authors contributed equally to the work\\

\textbf{Correspondance to:}\\
Timothée Poisot --- \texttt{timothee.poisot@umontreal.ca}\\

\vfill
This work is released by its authors under a CC-BY 4.0 license\hfill\ccby\\
Last revision: \emph{\today}

\clearpage
\thispagestyle{empty}

\vfill

        {\bfseries Purpose:}\,This template provides a series of scripts
to render a markdown document into an interactive website and a series
of PDFs.\\%
        {\bfseries Motivation:}\,It makes collaborating on text with
GitHub easier, and means that we never need to think about the
output.\\%
        {\bfseries Internals:}\,GitHub actions and a series of python
scritpts. The markdown is handled with \texttt{pandoc}.\\%

\vfill

\clearpage
\linenumbers
\pagestyle{normal}

\texttt{NCBITaxonomy.jl} is a package designed to facilitate the
reconciliation and cleaning of taxonomic names, using a local copy of
the NCBI taxonomic backbone (\textbf{Federhen2012NcbTax?};
\textbf{Schoch2020NcbTax?}); The basic search functions are coupled with
quality-of-life functions including case-insensitive search and custom
fuzzy string matching to facilitate the amount of information that can
be extracted automatically while allowing efficient manual curation and
inspection of results. \texttt{NCBITaxonomy.jl} works with version 1.6
of the Julia programming language (\textbf{Bezanson2017JulFre?}), and
relies on the Apache Arrow format to store a local copy of the NCBI raw
taxonomy files. The design of \texttt{NCBITaxonomy.jl} has been inspired
by similar efforts, like the R package \texttt{taxadb}
(\textbf{Norman2020TaxHig?}), which provides an offline alternative to
packages like \texttt{taxize} (\textbf{Chamberlain2013TaxTax?}).

\hypertarget{statement-of-need}{%
\section{Statement of need}\label{statement-of-need}}

Unambiguously identifying species is a far more challenging task than it
may appear. There are a vast number of reasons for this. Different
databases keep different taxonomic ``backbones,'' \emph{i.e.} different
data structures in which names are mapped to species, and organised in a
hierarchy. Not all names are unique identifiers to groups. For example,
\emph{Io} can either refer to a genus of plants from the aster family,
or to a genus of molluscs; the genus \emph{Mus} (of which the house
mouse \emph{Mus musculus} is a species), contains a sub-genus
\emph{also} named \emph{Mus}. Conversely, the same species can have
several names, which are valid synonyms: for example, the domestic cow
\emph{Bos taurus} admits \emph{Bos primigenius taurus} as a valid
synonym. Taxonomic nomenclature also changes regularly, with groups
being split, merged, or moved to a new position in the tree of life;
this is, notably, a common occurrence with viral taxonomy, each
subsequent version of which can differ markedly from the last; compare,
\emph{e.g} (\textbf{Lefkowitz2018VirTax?}) to
(\textbf{Walker2020ChaVir?}).

To add to the complexity, one must also consider that most taxa names
are at some point manually typed, which has the potential to introduce
additional mistakes in raw data; it is likely to expect that such
mistakes may arise when attempting to write down the (perfectly valid)
names of the bacterial isolate known as \emph{Myxococcus
llanfairpwllgwyngyllgogerychwyrndrobwllllantysiliogogogochensis}, or of
the crowned slaty flycatcher \emph{Griseotyrannus
aurantioatrocristatus}. These mistakes are more likely when dealing with
hyper-diverse samples, like plant census (\textbf{Dauncey2016ComMis?};
\textbf{Wagner2016RevSof?}; \textbf{Conti2021MatAlg?}). In addition to
binomial names, the same species can be known by many vernacular
(common) names, which are language or even region-specific: \emph{Ovis
aries}, for example, has valid English vernaculars including lamb,
sheep, wild sheep, and domestic sheep.

All these considerations are actually important when matching species
names both within and across datasets. Let us consider the following
species survey of individual fishes, European chub, \emph{Cyprinus
cephalus}, \emph{Leuciscus cephalus}, \emph{Squalius cephalus}: all are
the same species (\emph{S. cephalus}), referred to as one of the
vernacular (European chub) and two formerly accepted names now
classified as synonyms. A cautious estimate of diversity based on the
user-supplied names would give \(n=4\) species, when there is in fact
only one.

A package with the ability to handle the sources of errors outlined
above, and especially while provide an authoritative classification, can
accelerate the work of consuming large volumes of biodiversity data. For
example, this package was used in the process of developing the
\emph{CLOVER} database (\textbf{Gibb2021DatPro?}) of host-virus
associations, by reconciling the names of viruses and mammals from four
different sources, where all of the issues described above were present.

\hypertarget{overview-of-functionalities}{%
\section{Overview of
functionalities}\label{overview-of-functionalities}}

An up-to-date version of the documentation for \texttt{NCBITaxonomy.jl}
can be found online at
\url{https://docs.ecojulia.org/NCBITaxonomy.jl/stable/}, including
examples and a documentation of every method. The package is released
under the MIT license. Contributions can be made in the form of issues
(bug reports, questions, features suggestions) and pull requests. The
package can be checked out and installed anonymously from the central
Julia repository:

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{using}\NormalTok{ Pkg}

\CommentTok{\# This line should go in the Julia configuration file {-} note that the path}
\CommentTok{\# will be created if it doesn\textquotesingle{}t exist, and will be used to store the}
\CommentTok{\# raw taxonomic table}
\ConstantTok{ENV}\NormalTok{[}\StringTok{"NCBITAXONOMY\_PATH"}\NormalTok{] }\OperatorTok{=}\NormalTok{ joinpath(homedir()}\OperatorTok{,} \StringTok{"data"}\OperatorTok{,} \StringTok{"NCBITaxonomy.jl"}\NormalTok{)}

\NormalTok{Pkg.add(}\StringTok{"NCBITaxonomy"}\NormalTok{) }\CommentTok{\# Dowloading the files may take a long time}
\end{Highlighting}
\end{Shaded}

The package will download the most recent version of the NCBI taxonomy
database, and transform in into a set of Apache Arrow files ready for
use. Note that the \texttt{NCBITAXONOMY\_PATH} can specified on a
per-project basis, and as long as the package is not re-built, the local
set of tables downloaded from NCBI will not change; this way, users can
re-run an analysis with a guarantee that the underlying taxonomic
backbone has not changed.

\hypertarget{improved-name-matching}{%
\subsection{Improved name matching}\label{improved-name-matching}}

Name finding is primarily done through the \texttt{taxon} function,
which admits either a unique NCBI identifier (\emph{e.g.}
\texttt{taxon(36219)} for the bogue \emph{Boops boops}), a string
(\texttt{taxon("Boops\ boops")}), or a data frame with a restricted list
of names (see the next section). The \texttt{taxon} method has
additional arguments to perform fuzzy matching in order to catch
possible typos (\texttt{taxon("Boops\ bops";\ strict=false)}), to
perform a lowercase search (useful when alphanumeric codes are part of
the taxon name, like for some viruses), and to restrict the the search
to a specific taxonomic rank.

The lowercase search can be a preferable alternative to fuzzy string
matching. Consider the string \texttt{Adeno-associated\ virus\ 3b} - it
has three names with equal distance (under the Levensthein string
distance function):

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{julia}\OperatorTok{\textgreater{}}\NormalTok{ similarnames(}\StringTok{"Adeno{-}associated virus 3b"}\OperatorTok{;}\NormalTok{ threshold}\OperatorTok{=}\FloatTok{0.95}\NormalTok{)}
\FloatTok{3}\OperatorTok{{-}}\NormalTok{element }\DataTypeTok{Vector}\NormalTok{\{}\DataTypeTok{Pair}\NormalTok{\{NCBITaxon}\OperatorTok{,} \DataTypeTok{Float64}\NormalTok{\}\}}\OperatorTok{:}
\NormalTok{  Adeno}\OperatorTok{{-}}\NormalTok{associated virus }\OperatorTok{{-}} \FloatTok{3}\NormalTok{ (ncbi}\OperatorTok{:}\FloatTok{46350}\NormalTok{) }\OperatorTok{=\textgreater{}} \FloatTok{0.96}
\NormalTok{   Adeno}\OperatorTok{{-}}\NormalTok{associated virus }\FloatTok{3}\NormalTok{B (ncbi}\OperatorTok{:}\FloatTok{68742}\NormalTok{) }\OperatorTok{=\textgreater{}} \FloatTok{0.96}
\NormalTok{ Adeno}\OperatorTok{{-}}\NormalTok{associated virus }\FloatTok{3}\NormalTok{A (ncbi}\OperatorTok{:}\FloatTok{1406223}\NormalTok{) }\OperatorTok{=\textgreater{}} \FloatTok{0.96}
\end{Highlighting}
\end{Shaded}

Depending on the operating system, either of these three names can be
returned; compare to the output of a case insensitive name search:

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{julia}\OperatorTok{\textgreater{}}\NormalTok{ taxon(}\StringTok{"Adeno{-}associated virus 3b"}\OperatorTok{;}\NormalTok{ casesensitive}\OperatorTok{=}\ExtensionTok{false}\NormalTok{)}
\NormalTok{Adeno}\OperatorTok{{-}}\NormalTok{associated virus }\FloatTok{3}\NormalTok{B (ncbi}\OperatorTok{:}\FloatTok{68742}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

This returns the correct name.

\hypertarget{name-matching-output-and-error-handling}{%
\subsection{Name matching output and error
handling}\label{name-matching-output-and-error-handling}}

The \texttt{taxon} function will either return a \texttt{NCBITaxon}
object (made of a \texttt{name} and \texttt{id}), or throw either a
\texttt{NameHasNoDirectMatch} (with instructions about how to possible
solve it, using the \texttt{similarnames} function), or a
\texttt{NameHasMultipleMatches} (listing the possible valid matches, and
suggesting to use \texttt{alternativetaxa} to find the correct one).
Therefore, the common way to work with the \texttt{taxon} function would
be to wrap it in a \texttt{try}/\texttt{catch} statement:

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{try}
\NormalTok{  taxon(name)}
  \CommentTok{\# Additional operations with the matched name}
\KeywordTok{catch}\NormalTok{ err}
  \KeywordTok{if}\NormalTok{ isa(err}\OperatorTok{,}\NormalTok{ NameHasNoDirectMatch)}
    \CommentTok{\# What to do if no match is found}
  \KeywordTok{elseif}\NormalTok{ isa(err}\OperatorTok{,}\NormalTok{ NameHasMultipleMatches)}
    \CommentTok{\# What to do if there are multiple matches}
  \KeywordTok{else}
    \CommentTok{\# What to do in case of another error that is not NCBITaxonomy specific}
  \KeywordTok{end}
\KeywordTok{end}
\end{Highlighting}
\end{Shaded}

These functions will not demand any user input in the form of key
presses (though they can be wrapped in additional code to allow it), as
they are intended to run on clusters without supervision. The
\texttt{taxon} function has good scaling using muliple threads. For
convenience in rapidly getting a taxon for demonstration purposes, we
also provide a string macro, whereby \emph{e.g.}
\texttt{ncbi"Procyon\ lotor"} will return the taxon object for the
raccoon.

\hypertarget{name-filtering-functions}{%
\subsection{Name filtering functions}\label{name-filtering-functions}}

As the full NCBI names table has over 3 million entries at the time of
writing, we have provided a number of functions to restrict the scope of
names that are searched. These are driven by the NCBI \emph{divisions}.
For example \texttt{nf\ =\ mammalfilter(true)} will return a data frame
containing the names of mammals, inclusive of rodents and primates, and
can be used with \emph{e.g.} \texttt{taxon(nf,\ "Pan")}. This has the
dual advantage of making search faster, but also of avoiding matching on
names that are shared by another taxonomic group (which is not an issue
with \emph{Pan}, but is an issue with \emph{e.g.} \emph{Io} as mentioned
in the introduction).

Note that the use of a restricted list of names can have significant
performance consequences: compare, for example, the time taken to return
the taxon \emph{Pan} (ID 9596) in the entire database, in all mammals,
and in all primates:

\begin{longtable}[]{@{}lclll@{}}
\toprule
Names list & Fuzzy matching & Time (ms) & Allocations & Memory
allocated\tabularnewline
\midrule
\endhead
all & no & 23 & 34 & 2 KiB\tabularnewline
& yes & 105 & 2580 & 25 MiB\tabularnewline
\texttt{mammalfilter(true)} & no & 0.55 & 32 & 2 KiB\tabularnewline
& yes & 1.9 & 551 & 286 KiB\tabularnewline
\texttt{primatefilter()} & no & 0.15 & 33 & 2 KiB\tabularnewline
& yes & 0.3 & 92 & 27 KiB\tabularnewline
\bottomrule
\end{longtable}

Clearly, the optimal search strategy is to (i) rely on name filters to
ensure that search are conducted within the appropriate NCBI division,
and (ii) only rely on fuzzy matching when the strict or lowercase match
fails to return a name, as fuzzy matching can result in order of
magnitude more run time and memory footprint. These numbers were
obtained on a single Intel i7-8665U CPU (@ (1.90GHz). Using
\texttt{"chimpanzees"} as the search string (the NCBI recognized
vernacular for \emph{Pan}) gave qualitatively similar results,
suggesting that there is no performance cost associated with working
with synonyms or verncular input data.

\hypertarget{quality-of-life-functions}{%
\subsection{Quality of life functions}\label{quality-of-life-functions}}

In order to facilitate working with names, we provide the
\texttt{authority} function (gives the full taxonomic authority for a
name), \texttt{synonyms} (to get alternative valid names),
\texttt{vernacular} (for English common names), and \texttt{rank} (for
the taxonomic rank).

\hypertarget{taxonomic-lineages-navigation}{%
\subsection{Taxonomic lineages
navigation}\label{taxonomic-lineages-navigation}}

The \texttt{children} function will return all nodes that are directly
descended from a taxon; the \texttt{descendants} function will
recursively apply this function to all descendants of these nodes, until
only terminal leaves are reached. The \texttt{parent} function is an
``upwards'' equivalent, giving that taxon from which a taxon descents;
the \texttt{lineage} function chains calls to \texttt{parent} until
either \texttt{taxon(1)} (the taxonomy root) or an arbitrary ancestor is
reached.

The \texttt{taxonomicdistance} function (and its in-place equivalent,
\texttt{taxonomicdistance!}, which uses memory-efficient re-allocation
if the user needs to change the distance between taxonomic ranks) uses
the (\textbf{Shimatani2001MeaSpe?}) approach to reconstruct a matrix of
distances based on taxonomy, which can serve as a rough proxy when no
phylogenies are available.

\textbf{Acknowledgements:} This work was supported by funding to the
Viral Emergence Research Initiative (VERENA) consortium including NSF
BII 2021909 and a grant from Institut de Valorisation des Données
(IVADO), by the NSERC Discovery Grants and Discovery Acceleration
Supplement programs, and by a donation from the Courtois Foundation.
Benchmarking of this package on distributed systems was enabled by
support provided by Calcul Québec (\texttt{www.calculquebec.ca}) and
Compute Canada (\texttt{www.computecanada.ca}). TP wrote the initial
code, TP and CJC contributed to API design, and all authors contributed
to functionalities and usability testing.

\hypertarget{references}{%
\section{References}\label{references}}

\end{document}

### 2021-10-14 preprint.tex
Deploying to gh-pages from @ PoisotLab/ms_ncbitaxonomy_softwarenote@6e49d36327da7c3212c875fbbe50627e080e7616 🚀

--- 2021-10-14 draft.tex
@@
 %!TEX TS-program = xelatex
-\documentclass[11pt]{article}
+\documentclass[10pt,oneside]{article}
+\usepackage[fontsize=9pt]{scrextend}
 
@@
 \newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth}{#1}}
-\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}\geometry{verbose,letterpaper,tmargin=2.2cm,bmargin=2.2cm,lmargin=2.2cm,rmargin=2.2cm}
+\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}\usepackage[table,dvipsnames]{xcolor}
 
-\usepackage{lineno}
-\usepackage[nolists,noheads]{endfloat}
+\geometry{includemp,
+            letterpaper,
+            top=2.4cm,
+            bottom=2.4cm,
+            left=1.0cm,
+            right=1.0cm,
+            marginparwidth=5cm,
+            marginparsep=1.0cm}
+
+\usepackage[singlelinecheck=off]{caption}
+
+\captionsetup{
+  font={small},
+  labelfont={bf},
+  format=plain,
+  labelsep=quad
+}
+
+\usepackage{floatrow}
+
+\floatsetup[figure]{margins=hangright,
+              facing=no,
+              capposition=beside,
+              capbesideposition={center,outside},
+              floatwidth=\textwidth}
+
+% \floatsetup[table]{margins=hangright,
+%              facing=no,
+%              capposition=beside,
+%              capbesideposition={center,outside},
+%              floatwidth=\textwidth}
 
@@
 
-\tolerance=1
-\emergencystretch=\maxdimen
-\hyphenpenalty=10000
-\hbadness=10000
+\setcounter{secnumdepth}{5}
 
-\doublespacing
+\usepackage{titlesec}
+
+\titleformat{\section}[block]
+{\normalfont\large\sffamily}
+{\thesection}{.5em}{\titlerule\\[.8ex]\bfseries}
+
+\titleformat{\subsection}[runin]
+{\normalfont\fontseries{b}\selectfont\filright\sffamily}
+{\thesubsection.}{.5em}{}
+
+\titleformat{\subsubsection}[runin]
+{\normalfont\itshape\rmfamily\bfseries}{\thesubsubsection}{1em}{}
+
+\fancypagestyle{firstpage}
+{
+   \fancyhf{}
+   \renewcommand{\headrulewidth}{0pt}
+   \fancyfoot[R]{\footnotesize\ccby}
+   \fancyfoot[L]{\footnotesize\sffamily\today}
+}
 
@@
 }
+
+\usepackage{tikz}
 \begin{document}
-\raggedright
-\thispagestyle{empty}
-{\Large\bfseries\sffamily Template to prepare preprints and manuscripts
-using markdown and github actions}
-\vskip 5em
+\tikz [remember picture, overlay] %
+\node [shift={(-0.6in,1.1cm)},scale=0.2,opacity=0.4] at (current page.south east)[anchor=south east]{\includegraphics{logo}};%
+\pagestyle{normal}
+\thispagestyle{firstpage}
 
+\newcommand{\colorRule}[3][black]{\textcolor[HTML]{#1}{\rule{#2}{#3}}}
+
+\noindent {\LARGE \textbf{\textsf{Template to prepare preprints and
+manuscripts using markdown and github actions}}}
+
+\medskip
+\begin{flushleft}
+{\small
 %
@@
 %
-\,\textsuperscript{1,2,‡}\quad %
+\,\textsuperscript{1,2,‡}, %
 Peregrin\,Took%
 %
-\,\textsuperscript{3,4}\quad %
+\,\textsuperscript{3,4}, %
 Merriadoc\,Brandybuck%
@@
 \,\textsuperscript{5,4,‡}
-
-\textsuperscript{1}\,Université de
-Montréal\quad \textsuperscript{2}\,Québec Centre for Biodiversity
-Sciences\quad \textsuperscript{3}\,Inn of the Prancing
-Pony\quad \textsuperscript{4}\,Fellowship of the
-Ring\quad \textsuperscript{5}\,Green Dragon Inn
-
+\vskip 1em
+\textsuperscript{1}\,Université de Montréal; \textsuperscript{2}\,Québec
+Centre for Biodiversity Sciences; \textsuperscript{3}\,Inn of the
+Prancing Pony; \textsuperscript{4}\,Fellowship of the
+Ring; \textsuperscript{5}\,Green Dragon Inn\\
 \textsuperscript{‡}\,These authors contributed equally to the work\\
-
+\vskip 1em
 \textbf{Correspondance to:}\\
 Timothée Poisot --- \texttt{timothee.poisot@umontreal.ca}\\
+}
+\end{flushleft}
 
-\vfill
-This work is released by its authors under a CC-BY 4.0 license\hfill\ccby\\
-Last revision: \emph{\today}
+\vskip 2em
+\makebox[0pt][l]{\colorRule[CCCCCC]{2.0\textwidth}{0.5pt}}
+\vskip 2em
+\noindent
 
-\clearpage
-\thispagestyle{empty}
-
-\vfill
+\marginpar{\vskip 1em\flushright
+{\small{\bfseries Keywords}:\par
+pandoc\\pandoc-crossref\\github actions\\}
+}
 
@@
 
-\vfill
-
-\clearpage
-\linenumbers
-\pagestyle{normal}
+\vskip 2em
+\makebox[0pt][l]{\colorRule[CCCCCC]{2.0\textwidth}{0.5pt}}
+\vskip 2em
 

### 2021-10-14 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_ncbitaxonomy_softwarenote@bdd677dbefd212c196af0b3f347485d670f31ef2 🚀

@@
 reconciliation and cleaning of taxonomic names, using a local copy of
-the NCBI taxonomic backbone (\textbf{Federhen2012NcbTax?};
-\textbf{Schoch2020NcbTax?}); The basic search functions are coupled with
-quality-of-life functions including case-insensitive search and custom
-fuzzy string matching to facilitate the amount of information that can
-be extracted automatically while allowing efficient manual curation and
-inspection of results. \texttt{NCBITaxonomy.jl} works with version 1.6
-of the Julia programming language (\textbf{Bezanson2017JulFre?}), and
-relies on the Apache Arrow format to store a local copy of the NCBI raw
-taxonomy files. The design of \texttt{NCBITaxonomy.jl} has been inspired
-by similar efforts, like the R package \texttt{taxadb}
-(\textbf{Norman2020TaxHig?}), which provides an offline alternative to
-packages like \texttt{taxize} (\textbf{Chamberlain2013TaxTax?}).
+the NCBI taxonomic backbone (Federhen 2012; Schoch \emph{et al.} 2020);
+The basic search functions are coupled with quality-of-life functions
+including case-insensitive search and custom fuzzy string matching to
+facilitate the amount of information that can be extracted automatically
+while allowing efficient manual curation and inspection of results.
+\texttt{NCBITaxonomy.jl} works with version 1.6 of the Julia programming
+language (Bezanson \emph{et al.} 2017), and relies on the Apache Arrow
+format to store a local copy of the NCBI raw taxonomy files. The design
+of \texttt{NCBITaxonomy.jl} has been inspired by similar efforts, like
+the R package \texttt{taxadb} (Norman \emph{et al.} 2020), which
+provides an offline alternative to packages like \texttt{taxize}
+(Chamberlain \& Szöcs 2013).
 
@@
 subsequent version of which can differ markedly from the last; compare,
-\emph{e.g} (\textbf{Lefkowitz2018VirTax?}) to
-(\textbf{Walker2020ChaVir?}).
+\emph{e.g} Lefkowitz \emph{et al.} (2018) to Walker \emph{et al.}
+(2020).
 
@@
 aurantioatrocristatus}. These mistakes are more likely when dealing with
-hyper-diverse samples, like plant census (\textbf{Dauncey2016ComMis?};
-\textbf{Wagner2016RevSof?}; \textbf{Conti2021MatAlg?}). In addition to
-binomial names, the same species can be known by many vernacular
-(common) names, which are language or even region-specific: \emph{Ovis
-aries}, for example, has valid English vernaculars including lamb,
-sheep, wild sheep, and domestic sheep.
+hyper-diverse samples, like plant census (Dauncey \emph{et al.} 2016;
+Wagner 2016; Conti \emph{et al.} 2021). In addition to binomial names,
+the same species can be known by many vernacular (common) names, which
+are language or even region-specific: \emph{Ovis aries}, for example,
+has valid English vernaculars including lamb, sheep, wild sheep, and
+domestic sheep.
 
@@
 example, this package was used in the process of developing the
-\emph{CLOVER} database (\textbf{Gibb2021DatPro?}) of host-virus
+\emph{CLOVER} database (Gibb \emph{et al.} 2021) of host-virus
 associations, by reconciling the names of viruses and mammals from four
@@
 if the user needs to change the distance between taxonomic ranks) uses
-the (\textbf{Shimatani2001MeaSpe?}) approach to reconstruct a matrix of
-distances based on taxonomy, which can serve as a rough proxy when no
-phylogenies are available.
+the Shimatani (2001) approach to reconstruct a matrix of distances based
+on taxonomy, which can serve as a rough proxy when no phylogenies are
+available.
 
@@
 \hypertarget{references}{%
-\section{References}\label{references}}
+\section*{References}\label{references}}
+\addcontentsline{toc}{section}{References}
+
+\hypertarget{refs}{}
+\begin{CSLReferences}{1}{0}
+\leavevmode\hypertarget{ref-Bezanson2017JulFre}{}%
+Bezanson, J., Edelman, A., Karpinski, S. \& Shah, V. (2017). Julia: A
+Fresh Approach to Numerical Computing. \emph{SIAM Review}, 59, 65--98.
+
+\leavevmode\hypertarget{ref-Chamberlain2013TaxTax}{}%
+Chamberlain, S.A. \& Szöcs, E. (2013). Taxize: Taxonomic search and
+retrieval in R. \emph{F1000Research}, 2, 191.
+
+\leavevmode\hypertarget{ref-Conti2021MatAlg}{}%
+Conti, M., Nimis, P.L. \& Martellos, S. (2021). Match Algorithms for
+Scientific Names in FlorItaly, the Portal to the Flora of Italy.
+\emph{Plants}, 10, 974.
+
+\leavevmode\hypertarget{ref-Dauncey2016ComMis}{}%
+Dauncey, E.A., Irving, J., Allkin, R. \& Robinson, N. (2016). Common
+mistakes when using plant names and how to avoid them. \emph{European
+Journal of Integrative Medicine}, 8, 597--601.
+
+\leavevmode\hypertarget{ref-Federhen2012NcbTax}{}%
+Federhen, S. (2012). The NCBI taxonomy database. \emph{Nucleic acids
+research}, 40, D136--D143.
+
+\leavevmode\hypertarget{ref-Gibb2021DatPro}{}%
+Gibb, R., Albery, G.F., Becker, D.J., Brierley, L., Connor, R., Dallas,
+T.A., \emph{et al.} (2021). Data proliferation, reconciliation, and
+synthesis in viral ecology. \emph{bioRxiv}, 2021.01.14.426572.
+
+\leavevmode\hypertarget{ref-Lefkowitz2018VirTax}{}%
+Lefkowitz, E.J., Dempsey, D.M., Hendrickson, R.C., Orton, R.J., Siddell,
+S.G. \& Smith, D.B. (2018). Virus taxonomy: The database of the
+International Committee on Taxonomy of Viruses (ICTV). \emph{Nucleic
+Acids Research}, 46, D708--D717.
+
+\leavevmode\hypertarget{ref-Norman2020TaxHig}{}%
+Norman, K.E.A., Chamberlain, S. \& Boettiger, C. (2020). Taxadb: A
+high-performance local taxonomic database interface. \emph{Methods in
+Ecology and Evolution}, 11, 1153--1159.
+
+\leavevmode\hypertarget{ref-Schoch2020NcbTax}{}%
+Schoch, C.L., Ciufo, S., Domrachev, M., Hotton, C.L., Kannan, S.,
+Khovanskaya, R., \emph{et al.} (2020). NCBI Taxonomy: A comprehensive
+update on curation, resources and tools. \emph{Database}, 2020.
+
+\leavevmode\hypertarget{ref-Shimatani2001MeaSpe}{}%
+Shimatani, K. (2001). On the Measurement of Species Diversity
+Incorporating Species Differences. \emph{Oikos}, 93, 135--147.
+
+\leavevmode\hypertarget{ref-Wagner2016RevSof}{}%
+Wagner, V. (2016). A review of software tools for spell-checking taxon
+names in vegetation databases. \emph{Journal of Vegetation Science}, 27,
+1323--1327.
+
+\leavevmode\hypertarget{ref-Walker2020ChaVir}{}%
+Walker, P.J., Siddell, S.G., Lefkowitz, E.J., Mushegian, A.R.,
+Adriaenssens, E.M., Dempsey, D.M., \emph{et al.} (2020). Changes to
+virus taxonomy and the Statutes ratified by the International Committee
+on Taxonomy of Viruses (2020). \emph{Archives of Virology}, 165,
+2737--2748.
+
+\end{CSLReferences}
 

### 2021-10-14 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_ncbitaxonomy_softwarenote@d3cea5b5fa2df44d44b68a798cacd1e9358e28d6 🚀

@@
 \thispagestyle{empty}
-{\Large\bfseries\sffamily Template to prepare preprints and manuscripts
-using markdown and github actions}
+{\Large\bfseries\sffamily NCBITaxonomy.jl - rapid biological names
+finding and reconciliation}
 \vskip 5em
@@
 %
-\,\textsuperscript{1,2,‡}\quad %
-Peregrin\,Took%
+\,\textsuperscript{1,2}\quad %
+\href{https://orcid.org/0000-0002-0965-1649}{Rory\,Gibb}%
 %
 \,\textsuperscript{3,4}\quad %
-Merriadoc\,Brandybuck%
+\href{https://orcid.org/0000-0002-4308-6321}{Sadie J.\,Ryan}%
 %
-\,\textsuperscript{5,4,‡}
+\,\textsuperscript{5,6,7}\quad %
+\href{https://orcid.org/0000-0001-6960-8434}{Colin J.\,Carlson}%
+%
+\,\textsuperscript{8,9}
 
-\textsuperscript{1}\,Université de
-Montréal\quad \textsuperscript{2}\,Québec Centre for Biodiversity
-Sciences\quad \textsuperscript{3}\,Inn of the Prancing
-Pony\quad \textsuperscript{4}\,Fellowship of the
-Ring\quad \textsuperscript{5}\,Green Dragon Inn
-
-\textsuperscript{‡}\,These authors contributed equally to the work\\
+\textsuperscript{1}\,Université de Montréal, Départment de Sciences
+Biologiques, Montréal QC, Canada\quad \textsuperscript{2}\,Québec Centre
+for Biodiversity Science, Montréal, QC,
+Canada\quad \textsuperscript{3}\,Centre on Climate Change and Planetary
+Health, London School of Hygiene and Tropical Medicine, London,
+UK\quad \textsuperscript{4}\,Centre for Mathematical Modelling of
+Infectious Diseases, London School of Hygiene and Tropical Medicine,
+London, UK\quad \textsuperscript{5}\,Emerging Pathogens Institute,
+University of Florida, Gainesville, FL, United States of
+America\quad \textsuperscript{6}\,School of Life Sciences, University of
+KwaZulu-Natal, Durban, South Africa\quad \textsuperscript{7}\,Department
+of Geography, University of Florida, Gainesville, FL, United States of
+America\quad \textsuperscript{8}\,Department of Microbiology and
+Immunology, Georgetown University Medical Center, Georgetown University,
+Washington, D.C., United States of
+America\quad \textsuperscript{9}\,Center for Global Health Science and
+Security, Georgetown University Medical Center, Georgetown University,
+Washington, D.C., United States of America
 
@@
 \vfill
-
-        {\bfseries Purpose:}\,This template provides a series of scripts
-to render a markdown document into an interactive website and a series
-of PDFs.\\%
-        {\bfseries Motivation:}\,It makes collaborating on text with
-GitHub easier, and means that we never need to think about the
-output.\\%
-        {\bfseries Internals:}\,GitHub actions and a series of python
-scritpts. The markdown is handled with \texttt{pandoc}.\\%
+\texttt{NCBITaxonomy.jl} is a package designed to facilitate the
+reconciliation and cleaning of taxonomic names, using a local copy of
+the NCBI taxonomic backbone (Federhen 2012, Schoch et al. 2020); The
+basic search functions are coupled with quality-of-life functions
+including case-insensitive search and custom fuzzy string matching to
+facilitate the amount of information that can be extracted automatically
+while allowing efficient manual curation and inspection of results.
+\texttt{NCBITaxonomy.jl} works with version 1.6 of the Julia programming
+language (Bezanson et al. 2017), and relies on the Apache Arrow format
+to store a local copy of the NCBI raw taxonomy files. The design of
+\texttt{NCBITaxonomy.jl} has been inspired by similar efforts, like the
+R package \texttt{taxadb} (Norman et al. 2020), which provides an
+offline alternative to packages like \texttt{taxize} (Chamberlain and
+Szöcs 2013).
 
@@
 reconciliation and cleaning of taxonomic names, using a local copy of
-the NCBI taxonomic backbone (Federhen 2012; Schoch \emph{et al.} 2020);
-The basic search functions are coupled with quality-of-life functions
+the NCBI taxonomic backbone (Federhen 2012, Schoch et al. 2020); The
+basic search functions are coupled with quality-of-life functions
 including case-insensitive search and custom fuzzy string matching to
@@
 \texttt{NCBITaxonomy.jl} works with version 1.6 of the Julia programming
-language (Bezanson \emph{et al.} 2017), and relies on the Apache Arrow
-format to store a local copy of the NCBI raw taxonomy files. The design
-of \texttt{NCBITaxonomy.jl} has been inspired by similar efforts, like
-the R package \texttt{taxadb} (Norman \emph{et al.} 2020), which
-provides an offline alternative to packages like \texttt{taxize}
-(Chamberlain \& Szöcs 2013).
+language (Bezanson et al. 2017), and relies on the Apache Arrow format
+to store a local copy of the NCBI raw taxonomy files. The design of
+\texttt{NCBITaxonomy.jl} has been inspired by similar efforts, like the
+R package \texttt{taxadb} (Norman et al. 2020), which provides an
+offline alternative to packages like \texttt{taxize} (Chamberlain and
+Szöcs 2013).
 
@@
 subsequent version of which can differ markedly from the last; compare,
-\emph{e.g} Lefkowitz \emph{et al.} (2018) to Walker \emph{et al.}
-(2020).
+\emph{e.g} Lefkowitz et al. (2018) to Walker et al. (2020).
 
@@
 aurantioatrocristatus}. These mistakes are more likely when dealing with
-hyper-diverse samples, like plant census (Dauncey \emph{et al.} 2016;
-Wagner 2016; Conti \emph{et al.} 2021). In addition to binomial names,
-the same species can be known by many vernacular (common) names, which
-are language or even region-specific: \emph{Ovis aries}, for example,
-has valid English vernaculars including lamb, sheep, wild sheep, and
+hyper-diverse samples, like plant census (Dauncey et al. 2016, Wagner
+2016, Conti et al. 2021). In addition to binomial names, the same
+species can be known by many vernacular (common) names, which are
+language or even region-specific: \emph{Ovis aries}, for example, has
+valid English vernaculars including lamb, sheep, wild sheep, and
 domestic sheep.
@@
 example, this package was used in the process of developing the
-\emph{CLOVER} database (Gibb \emph{et al.} 2021) of host-virus
-associations, by reconciling the names of viruses and mammals from four
-different sources, where all of the issues described above were present.
+\emph{CLOVER} database (Gibb et al. 2021) of host-virus associations, by
+reconciling the names of viruses and mammals from four different
+sources, where all of the issues described above were present.
 
@@
 \leavevmode\hypertarget{ref-Bezanson2017JulFre}{}%
-Bezanson, J., Edelman, A., Karpinski, S. \& Shah, V. (2017). Julia: A
-Fresh Approach to Numerical Computing. \emph{SIAM Review}, 59, 65--98.
+Bezanson, J. et al. 2017. Julia: A Fresh Approach to Numerical
+Computing. - SIAM Review 59: 65--98.
 
 \leavevmode\hypertarget{ref-Chamberlain2013TaxTax}{}%
-Chamberlain, S.A. \& Szöcs, E. (2013). Taxize: Taxonomic search and
-retrieval in R. \emph{F1000Research}, 2, 191.
+Chamberlain, S. A. and Szöcs, E. 2013. Taxize: Taxonomic search and
+retrieval in R. - F1000Research 2: 191.
 
 \leavevmode\hypertarget{ref-Conti2021MatAlg}{}%
-Conti, M., Nimis, P.L. \& Martellos, S. (2021). Match Algorithms for
-Scientific Names in FlorItaly, the Portal to the Flora of Italy.
-\emph{Plants}, 10, 974.
+Conti, M. et al. 2021. Match Algorithms for Scientific Names in
+FlorItaly, the Portal to the Flora of Italy. - Plants 10: 974.
 
 \leavevmode\hypertarget{ref-Dauncey2016ComMis}{}%
-Dauncey, E.A., Irving, J., Allkin, R. \& Robinson, N. (2016). Common
-mistakes when using plant names and how to avoid them. \emph{European
-Journal of Integrative Medicine}, 8, 597--601.
+Dauncey, E. A. et al. 2016. Common mistakes when using plant names and
+how to avoid them. - European Journal of Integrative Medicine 8:
+597--601.
 
 \leavevmode\hypertarget{ref-Federhen2012NcbTax}{}%
-Federhen, S. (2012). The NCBI taxonomy database. \emph{Nucleic acids
-research}, 40, D136--D143.
+Federhen, S. 2012. The NCBI taxonomy database. - Nucleic acids research
+40: D136--D143.
 
 \leavevmode\hypertarget{ref-Gibb2021DatPro}{}%
-Gibb, R., Albery, G.F., Becker, D.J., Brierley, L., Connor, R., Dallas,
-T.A., \emph{et al.} (2021). Data proliferation, reconciliation, and
-synthesis in viral ecology. \emph{bioRxiv}, 2021.01.14.426572.
+Gibb, R. et al. 2021. Data proliferation, reconciliation, and synthesis
+in viral ecology. - bioRxiv: 2021.01.14.426572.
 
 \leavevmode\hypertarget{ref-Lefkowitz2018VirTax}{}%
-Lefkowitz, E.J., Dempsey, D.M., Hendrickson, R.C., Orton, R.J., Siddell,
-S.G. \& Smith, D.B. (2018). Virus taxonomy: The database of the
-International Committee on Taxonomy of Viruses (ICTV). \emph{Nucleic
-Acids Research}, 46, D708--D717.
+Lefkowitz, E. J. et al. 2018. Virus taxonomy: The database of the
+International Committee on Taxonomy of Viruses (ICTV). - Nucleic Acids
+Research 46: D708--D717.
 
 \leavevmode\hypertarget{ref-Norman2020TaxHig}{}%
-Norman, K.E.A., Chamberlain, S. \& Boettiger, C. (2020). Taxadb: A
-high-performance local taxonomic database interface. \emph{Methods in
-Ecology and Evolution}, 11, 1153--1159.
+Norman, K. E. A. et al. 2020. Taxadb: A high-performance local taxonomic
+database interface. - Methods in Ecology and Evolution 11: 1153--1159.
 
 \leavevmode\hypertarget{ref-Schoch2020NcbTax}{}%
-Schoch, C.L., Ciufo, S., Domrachev, M., Hotton, C.L., Kannan, S.,
-Khovanskaya, R., \emph{et al.} (2020). NCBI Taxonomy: A comprehensive
-update on curation, resources and tools. \emph{Database}, 2020.
+Schoch, C. L. et al. 2020. NCBI Taxonomy: A comprehensive update on
+curation, resources and tools. - Database in press.
 
 \leavevmode\hypertarget{ref-Shimatani2001MeaSpe}{}%
-Shimatani, K. (2001). On the Measurement of Species Diversity
-Incorporating Species Differences. \emph{Oikos}, 93, 135--147.
+Shimatani, K. 2001. On the Measurement of Species Diversity
+Incorporating Species Differences. - Oikos 93: 135--147.
 
 \leavevmode\hypertarget{ref-Wagner2016RevSof}{}%
-Wagner, V. (2016). A review of software tools for spell-checking taxon
-names in vegetation databases. \emph{Journal of Vegetation Science}, 27,
+Wagner, V. 2016. A review of software tools for spell-checking taxon
+names in vegetation databases. - Journal of Vegetation Science 27:
 1323--1327.
@@
 \leavevmode\hypertarget{ref-Walker2020ChaVir}{}%
-Walker, P.J., Siddell, S.G., Lefkowitz, E.J., Mushegian, A.R.,
-Adriaenssens, E.M., Dempsey, D.M., \emph{et al.} (2020). Changes to
-virus taxonomy and the Statutes ratified by the International Committee
-on Taxonomy of Viruses (2020). \emph{Archives of Virology}, 165,
-2737--2748.
+Walker, P. J. et al. 2020. Changes to virus taxonomy and the Statutes
+ratified by the International Committee on Taxonomy of Viruses (2020). -
+Archives of Virology 165: 2737--2748.
 

### 2021-10-14 preprint.tex
Deploying to gh-pages from @ PoisotLab/ms_ncbitaxonomy_softwarenote@d3cea5b5fa2df44d44b68a798cacd1e9358e28d6 🚀

@@
 
-\noindent {\LARGE \textbf{\textsf{Template to prepare preprints and
-manuscripts using markdown and github actions}}}
+\noindent {\LARGE \textbf{\textsf{NCBITaxonomy.jl - rapid biological
+names finding and reconciliation}}}
 
@@
 %
-\,\textsuperscript{1,2,‡}, %
-Peregrin\,Took%
+\,\textsuperscript{1,2}, %
+\href{https://orcid.org/0000-0002-0965-1649}{Rory\,Gibb}%
 %
 \,\textsuperscript{3,4}, %
-Merriadoc\,Brandybuck%
+\href{https://orcid.org/0000-0002-4308-6321}{Sadie J.\,Ryan}%
 %
-\,\textsuperscript{5,4,‡}
+\,\textsuperscript{5,6,7}, %
+\href{https://orcid.org/0000-0001-6960-8434}{Colin J.\,Carlson}%
+%
+\,\textsuperscript{8,9}
 \vskip 1em
-\textsuperscript{1}\,Université de Montréal; \textsuperscript{2}\,Québec
-Centre for Biodiversity Sciences; \textsuperscript{3}\,Inn of the
-Prancing Pony; \textsuperscript{4}\,Fellowship of the
-Ring; \textsuperscript{5}\,Green Dragon Inn\\
-\textsuperscript{‡}\,These authors contributed equally to the work\\
+\textsuperscript{1}\,Université de Montréal, Départment de Sciences
+Biologiques, Montréal QC, Canada; \textsuperscript{2}\,Québec Centre for
+Biodiversity Science, Montréal, QC, Canada; \textsuperscript{3}\,Centre
+on Climate Change and Planetary Health, London School of Hygiene and
+Tropical Medicine, London, UK; \textsuperscript{4}\,Centre for
+Mathematical Modelling of Infectious Diseases, London School of Hygiene
+and Tropical Medicine, London, UK; \textsuperscript{5}\,Emerging
+Pathogens Institute, University of Florida, Gainesville, FL, United
+States of America; \textsuperscript{6}\,School of Life Sciences,
+University of KwaZulu-Natal, Durban, South
+Africa; \textsuperscript{7}\,Department of Geography, University of
+Florida, Gainesville, FL, United States of
+America; \textsuperscript{8}\,Department of Microbiology and Immunology,
+Georgetown University Medical Center, Georgetown University, Washington,
+D.C., United States of America; \textsuperscript{9}\,Center for Global
+Health Science and Security, Georgetown University Medical Center,
+Georgetown University, Washington, D.C., United States of America\\
 \vskip 1em
@@
 {\small{\bfseries Keywords}:\par
-pandoc\\pandoc-crossref\\github actions\\}
+biodiversity\\taxonomy\\NCBI\\fuzzy matching\\}
 }
 
-        {\bfseries Purpose:}\,This template provides a series of scripts
-to render a markdown document into an interactive website and a series
-of PDFs.\\%
-        {\bfseries Motivation:}\,It makes collaborating on text with
-GitHub easier, and means that we never need to think about the
-output.\\%
-        {\bfseries Internals:}\,GitHub actions and a series of python
-scritpts. The markdown is handled with \texttt{pandoc}.\\%
+\texttt{NCBITaxonomy.jl} is a package designed to facilitate the
+reconciliation and cleaning of taxonomic names, using a local copy of
+the NCBI taxonomic backbone (Federhen 2012, Schoch et al. 2020); The
+basic search functions are coupled with quality-of-life functions
+including case-insensitive search and custom fuzzy string matching to
+facilitate the amount of information that can be extracted automatically
+while allowing efficient manual curation and inspection of results.
+\texttt{NCBITaxonomy.jl} works with version 1.6 of the Julia programming
+language (Bezanson et al. 2017), and relies on the Apache Arrow format
+to store a local copy of the NCBI raw taxonomy files. The design of
+\texttt{NCBITaxonomy.jl} has been inspired by similar efforts, like the
+R package \texttt{taxadb} (Norman et al. 2020), which provides an
+offline alternative to packages like \texttt{taxize} (Chamberlain and
+Szöcs 2013).
 

### 2022-06-27 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_ncbitaxonomy_softwarenote@58ea496e72ccfdf2bc9f32e816918cad1487d934 🚀
Deploying to gh-pages from @ PoisotLab/ms_ncbitaxonomy_softwarenote@a0fd725e79a0798ad9322978f98274ab532f2319 🚀
Deploying to gh-pages from @ PoisotLab/ms_ncbitaxonomy_softwarenote@081468149df4bbeb8db27e61cfa7a7be121e2af1 🚀

@@
 
-\texttt{NCBITaxonomy.jl} is a package designed to facilitate the
-reconciliation and cleaning of taxonomic names, using a local copy of
-the NCBI taxonomic backbone (Federhen 2012, Schoch et al. 2020); The
-basic search functions are coupled with quality-of-life functions
-including case-insensitive search and custom fuzzy string matching to
-facilitate the amount of information that can be extracted automatically
-while allowing efficient manual curation and inspection of results.
-\texttt{NCBITaxonomy.jl} works with version 1.6 of the Julia programming
-language (Bezanson et al. 2017), and relies on the Apache Arrow format
-to store a local copy of the NCBI raw taxonomy files. The design of
-\texttt{NCBITaxonomy.jl} has been inspired by similar efforts, like the
-R package \texttt{taxadb} (Norman et al. 2020), which provides an
-offline alternative to packages like \texttt{taxize} (Chamberlain and
-Szöcs 2013).
-
-\hypertarget{statement-of-need}{%
-\section{Statement of need}\label{statement-of-need}}
-
 Unambiguously identifying species is a far more challenging task than it
@@
 mouse \emph{Mus musculus} is a species), contains a sub-genus
-\emph{also} named \emph{Mus}. Conversely, the same species can have
-several names, which are valid synonyms: for example, the domestic cow
-\emph{Bos taurus} admits \emph{Bos primigenius taurus} as a valid
-synonym. Taxonomic nomenclature also changes regularly, with groups
-being split, merged, or moved to a new position in the tree of life;
-this is, notably, a common occurrence with viral taxonomy, each
-subsequent version of which can differ markedly from the last; compare,
-\emph{e.g} Lefkowitz et al. (2018) to Walker et al. (2020).
+\emph{also} named \emph{Mus} (within which \emph{Mus musculus} is
+located). Conversely, the same species can have several names, which are
+valid synonyms: for example, the domestic cow \emph{Bos taurus} admits
+\emph{Bos primigenius taurus} as a valid synonym. In addition to
+binomial names, the same species can be known by many vernacular
+(common) names, which are language or even region-specific: \emph{Ovis
+aries}, for example, has valid English vernaculars including lamb,
+sheep, wild sheep, and domestic sheep.
+
+Finally, taxonomic nomenclature changes regularly, with groups being
+split, merged, or moved to a new position in the tree of life; this is,
+notably, a common occurrence with viral taxonomy, each subsequent
+version of which can differ markedly from the last; compare, \emph{e.g}
+Lefkowitz et al. (2018) to Walker et al. (2020), where entire viral
+sub-trees were split, re-organized, and created within just two years.
+These taxonomic changes have profound implications for the way we
+perceive biodiversity at global scales (Meier 2009), to the point were
+taxonomic revisions should sometimes be actively conducted to improve
+\emph{e.g.} conservation outcomes (Melville et al. 2021).
 
@@
 aurantioatrocristatus}. These mistakes are more likely when dealing with
-hyper-diverse samples, like plant census (Dauncey et al. 2016, Wagner
-2016, Conti et al. 2021). In addition to binomial names, the same
-species can be known by many vernacular (common) names, which are
-language or even region-specific: \emph{Ovis aries}, for example, has
-valid English vernaculars including lamb, sheep, wild sheep, and
-domestic sheep.
+hyper-diverse samples (demanding to memorize more names), like plant
+census (Dauncey et al. 2016, Wagner 2016, Conti et al. 2021); when
+dealing with multiple investigators with different knowledge of the
+taxonomy; and as a result of the estimated error in any data entry
+exercice, which other fields estimate at up to about 5\% (Barchard and
+Pace 2011).
 
@@
 An up-to-date version of the documentation for \texttt{NCBITaxonomy.jl}
-can be found online at
-\url{https://docs.ecojulia.org/NCBITaxonomy.jl/stable/}, including
-examples and a documentation of every method. The package is released
-under the MIT license. Contributions can be made in the form of issues
-(bug reports, questions, features suggestions) and pull requests. The
-package can be checked out and installed anonymously from the central
-Julia repository:
+can be found online from the EcoJulia documentation hub
+\href{https://docs.ecojulia.org/NCBITaxonomy.jl/stable/}{https://docs.ecojulia.org/},
+including examples and in-line documentation of every method. The
+package is released under the MIT license. Contributions can be made in
+the form of issues (bug reports, questions, features suggestions) and
+pull requests. The package can be checked out and installed anonymously
+from the central Julia repository:
 
@@
 \begin{CSLReferences}{1}{0}
+\leavevmode\hypertarget{ref-Barchard2011PreHum}{}%
+Barchard, K. and Pace, L. 2011. Preventing human error: The impact of
+data entry methods on data accuracy and statistical results. - Computers
+in Human Behavior 27: 1834--1839.
+
 \leavevmode\hypertarget{ref-Bezanson2017JulFre}{}%
@@
 \leavevmode\hypertarget{ref-Gibb2021DatPro}{}%
-Gibb, R. et al. 2021. Data proliferation, reconciliation, and synthesis
-in viral ecology. - bioRxiv: 2021.01.14.426572.
+Gibb, R. et al. 2021. Data Proliferation, Reconciliation, and Synthesis
+in Viral Ecology. - BioScience in press.
 
@@
 Research 46: D708--D717.
+
+\leavevmode\hypertarget{ref-Meier2009BioRes}{}%
+Meier, R. 2009. Biodiversity Research Based on Taxonomic Revisions - A
+Tale of Unrealized Opportunities -. - In: pp. 323--345.
+
+\leavevmode\hypertarget{ref-Melville2021RetApp}{}%
+Melville, J. et al. 2021. A return-on-investment approach for
+prioritization of rigorous taxonomic research needed to inform responses
+to the biodiversity crisis. - PLOS Biology 19: e3001210.
 

### 2022-06-27 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_ncbitaxonomy_softwarenote@9e37654d5cf3da8de7bf1978556b9f3a5e26afeb 🚀

@@
 
-All these considerations are actually important when matching species
-names both within and across datasets. Let us consider the following
-species survey of individual fishes, European chub, \emph{Cyprinus
-cephalus}, \emph{Leuciscus cephalus}, \emph{Squalius cephalus}: all are
+All these considerations become important when matching species names
+both within and across datasets. Let us consider the hypothetical
+species survey of riverine fishes: European chub, \emph{Cyprinus
+cephalus}, \emph{Leuciscus cephalus}, \emph{Squalius cephalus}. All are
 the same species (\emph{S. cephalus}), referred to as one of the
 vernacular (European chub) and two formerly accepted names now
-classified as synonyms. A cautious estimate of diversity based on the
-user-supplied names would give \(n=4\) species, when there is in fact
-only one.
+classified as synonyms (but still present in the litterature). A
+cautious estimate of diversity based on the user-supplied names would
+give \(n=4\) species, when there is in fact only one. When the size of
+biodiversity datasets increases, and notably when the taxonomic scope of
+these datasets explodes, including organisms for which ``names'' are a
+fuzzier concept (for example, \emph{Influenza A virus
+(A/Sydney/05/97-like(H3N2))} is a valid name for a common influenza
+strain, although one that lacks a taxonomic rank), the feasibility of
+manual curation decreases.
 
-A package with the ability to handle the sources of errors outlined
-above, and especially while provide an authoritative classification, can
-accelerate the work of consuming large volumes of biodiversity data. For
-example, this package was used in the process of developing the
-\emph{CLOVER} database (Gibb et al. 2021) of host-virus associations, by
+In this manuscript, we describe \texttt{NCBITaxonomy.jl}, a Julia
+package that provides advanced name matching and error handling
+capacities for the reconciliation of taxonomic names to the NCBI
+database. This package was used to facilitate the development of the
+\emph{CLOVER} (Gibb et al. 2021) database of host-virus associations, by
 reconciling the names of viruses and mammals from four different
-sources, where all of the issues described above were present.
+sources, where all of the issues described above were present. More
+recently, it has become part of the automated curation of data for the
+\emph{VIRION} (Carlson et al. 2022) database, which automatically
+curates an up-to-date, authoritative host-mammal network from dozens of
+heterogeneous sources. We describe the core capacities of this package,
+and highlight how it enables safe, high-performance name reconciliation.
 
@@
 the form of issues (bug reports, questions, features suggestions) and
-pull requests. The package can be checked out and installed anonymously
-from the central Julia repository:
+pull requests.
+
+In order to achieve good performance, the package will first retrieve
+the latest (as validated by its checksum) NCBI taxonomy backbone, store
+it locally, and pre-process it as a set of Julia data tables. By
+default, the taxonomy will be downloaded to the Julia package
+repository, which is not an ideal solution, and therefore we recommend
+that users set an environment variable to specificy where the data will
+be loaded from (this path will be created if it doesn't exist):
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\ConstantTok{ENV}\NormalTok{[}\StringTok{"NCBITAXONOMY\_PATH"}\NormalTok{] }\OperatorTok{=}\NormalTok{ joinpath(homedir()}\OperatorTok{,} \StringTok{"data"}\OperatorTok{,} \StringTok{"NCBITaxonomy.jl"}\NormalTok{)}
+\end{Highlighting}
+\end{Shaded}
+
+Note that this location can be different for different projects, as the
+package is able to update the taxoonmic backbone (and will indeed prompt
+the user to do so if the taxonomy is more than 90 days old). The package
+can then be checked out and installed anonymously from the central Julia
+repository:
 
@@
 \KeywordTok{using}\NormalTok{ Pkg}
-
-\CommentTok{\# This line should go in the Julia configuration file {-} note that the path}
-\CommentTok{\# will be created if it doesn\textquotesingle{}t exist, and will be used to store the}
-\CommentTok{\# raw taxonomic table}
-\ConstantTok{ENV}\NormalTok{[}\StringTok{"NCBITAXONOMY\_PATH"}\NormalTok{] }\OperatorTok{=}\NormalTok{ joinpath(homedir()}\OperatorTok{,} \StringTok{"data"}\OperatorTok{,} \StringTok{"NCBITaxonomy.jl"}\NormalTok{)}
-
 \NormalTok{Pkg.add(}\StringTok{"NCBITaxonomy"}\NormalTok{) }\CommentTok{\# Dowloading the files may take a long time}
@@
 
-The package will download the most recent version of the NCBI taxonomy
-database, and transform in into a set of Apache Arrow files ready for
-use. Note that the \texttt{NCBITAXONOMY\_PATH} can specified on a
-per-project basis, and as long as the package is not re-built, the local
-set of tables downloaded from NCBI will not change; this way, users can
-re-run an analysis with a guarantee that the underlying taxonomic
-backbone has not changed.
+As long as the package is not re-built, the local set of tables
+downloaded from NCBI will not change; this way, users can re-run an
+analysis with a guarantee that the underlying taxonomic backbone has not
+changed, which is not the case when relying on API queries. In order to
+update the taxonomic backbone, users can call the \texttt{build}
+function of Julia's package manager (\texttt{{]}build\ NCBITaxonomy}),
+which will download the most recent version of all files.
 
@@
 (\texttt{taxon("Boops\ boops")}), or a data frame with a restricted list
-of names (see the next section). The \texttt{taxon} method has
-additional arguments to perform fuzzy matching in order to catch
-possible typos (\texttt{taxon("Boops\ bops";\ strict=false)}), to
-perform a lowercase search (useful when alphanumeric codes are part of
-the taxon name, like for some viruses), and to restrict the the search
-to a specific taxonomic rank.
+of names in order to create a name finder function (see the next
+section). The \texttt{taxon} method has additional arguments to perform
+fuzzy matching in order to catch possible typos
+(\texttt{taxon("Boops\ bops";\ strict=false)}), to perform a lowercase
+search (useful when alphanumeric codes are part of the taxon name, like
+for some viruses), and to restrict the the search to a specific
+taxonomic rank. The \texttt{taxon} function also accepts a
+\texttt{preferscientificname} keyword, to prevent matching vernacular
+names; the use of this keyword ought to be informed by knowledge about
+how the data were entered.
 
@@
 
-Depending on the operating system, either of these three names can be
-returned; compare to the output of a case insensitive name search:
+Depending on the operating system (and specifically whether it is
+case-sensitive), either of these three names can be returned; compare to
+the output of a case insensitive name search:
 
@@
 
-The \texttt{taxon} function will either return a \texttt{NCBITaxon}
-object (made of a \texttt{name} and \texttt{id}), or throw either a
-\texttt{NameHasNoDirectMatch} (with instructions about how to possible
-solve it, using the \texttt{similarnames} function), or a
-\texttt{NameHasMultipleMatches} (listing the possible valid matches, and
-suggesting to use \texttt{alternativetaxa} to find the correct one).
+When it succeeds, \texttt{taxon} will return a \texttt{NCBITaxon} object
+(made of a \texttt{name} string field, and an \texttt{id} numerical
+field). That being said, the package is designed under the assumption
+that ambiguities should yield an error for the user to handle. There are
+two such errors: \texttt{NameHasNoDirectMatch} (with instructions about
+how to possible solve it, using the \texttt{similarnames} function), or
+a \texttt{NameHasMultipleMatches} (listing the possible valid matches,
+and suggesting to use \texttt{alternativetaxa} to find the correct one).
 Therefore, the common way to work with the \texttt{taxon} function would
@@
 presses (though they can be wrapped in additional code to allow it), as
-they are intended to run on clusters without supervision. The
-\texttt{taxon} function has good scaling using muliple threads. For
-convenience in rapidly getting a taxon for demonstration purposes, we
-also provide a string macro, whereby \emph{e.g.}
+they are intended to run on clusters or virtual machines without
+supervision. The \texttt{taxon} function has good scaling using muliple
+threads. For convenience in rapidly getting a taxon for demonstration
+purposes, we also provide a string macro, whereby \emph{e.g.}
 \texttt{ncbi"Procyon\ lotor"} will return the taxon object for the
@@
 with \emph{Pan}, but is an issue with \emph{e.g.} \emph{Io} as mentioned
-in the introduction).
+in the introduction, or with the common name \emph{Lizard}, which
+fuzzy-matches on the hemipteran genus \emph{Lisarda} rather than the
+class \emph{Lepidosauria}).
 
@@
 performance consequences: compare, for example, the time taken to return
-the taxon \emph{Pan} (ID 9596) in the entire database, in all mammals,
-and in all primates:
+the taxon \emph{Pan} in the entire database, in all mammals, and in all
+primates:
 
@@
 obtained on a single Intel i7-8665U CPU (@ (1.90GHz). Using
-\texttt{"chimpanzees"} as the search string (the NCBI recognized
-vernacular for \emph{Pan}) gave qualitatively similar results,
+\texttt{"chimpanzees"} as the search string (one of the NCBI recognized
+vernaculars for \emph{Pan}) gave qualitatively similar results,
 suggesting that there is no performance cost associated with working
@@
 \texttt{vernacular} (for English common names), and \texttt{rank} (for
-the taxonomic rank).
+the taxonomic rank). These functions are not used in name matching, but
+are often useful in the post-processing of results.
 
@@
 only terminal leaves are reached. The \texttt{parent} function is an
-``upwards'' equivalent, giving that taxon from which a taxon descents;
+``upwards'' equivalent, giving the taxon from which a taxon descends;
 the \texttt{lineage} function chains calls to \texttt{parent} until
@@
 on taxonomy, which can serve as a rough proxy when no phylogenies are
-available.
+available. This allows coarse estimations of taxonomic diversity based
+on species lists. The default distance between taxoonmic levels is as in
+Shimatani (2001) (\emph{i.e.} species have a distance of 0, genus of 1,
+family of 2, sbu-classes of 3, and everything else 4), but specific
+scores can be passed for \emph{any} taxonomic level know to the NCBI
+name table.
 
@@
 Computing. - SIAM Review 59: 65--98.
+
+\leavevmode\hypertarget{ref-Carlson2022GloVir}{}%
+Carlson, C. J. et al. 2022. The Global Virome in One Network (VIRION):
+An Atlas of Vertebrate-Virus Associations. - mBio in press.
 

### 2022-06-27 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_ncbitaxonomy_softwarenote@cb3b8649606ace1b96dd62265adf5afc9e3ad0c9 🚀

@@
 \emph{VIRION} (Carlson et al. 2022) database, which automatically
-curates an up-to-date, authoritative host-mammal network from dozens of
+curates an up-to-date, authoritative virome network from dozens of
 heterogeneous sources. We describe the core capacities of this package,
@@
 
+This software note describes version \texttt{v0.2.3} of the package (we
+follow semantic versioning), which works on Julia 1.5 upwards. The
+dependencies are all resolved by the package manager at installation,
+and (on the user-facing side) include the \texttt{StringDistances.jl}
+package, allowing users to experiment with different string matching
+methods. As is best practices for Julia packages, a
+\texttt{Project.toml} file specifying compatible dependencies versions
+is distributed with the package. The code is covered by unit-tests (with
+about 98\% coverage), as well as integration tests as part of the
+documentation (specifically, a use-case detailing how to clean data from
+a biodiversity survey, and a use-case aiming to reconstruct a taxonomic
+tree for the Lemuriformes).
+
 \hypertarget{improved-name-matching}{%
@@
 
-Name finding is primarily done through the \texttt{taxon} function,
-which admits either a unique NCBI identifier (\emph{e.g.}
+Name finding, \emph{i.e.} the matching of an arbitrary string to a
+taxonomic identifier, is primarily done through the \texttt{taxon}
+function, which admits either a unique NCBI identifier (\emph{e.g.}
 \texttt{taxon(36219)} for the bogue \emph{Boops boops}), a string
@@
 
+\hypertarget{conclusion}{%
+\section{Conclusion}\label{conclusion}}
+
+\texttt{NCBITaxonomy.jl} enables rapid, taxonomically-restricted,
+adaptive matching for taxonomic names. By implementing various
+combinations of search strategies, it allows users to (i) optimize the
+speed of their queries and (ii) avoid usual caveats of simple string
+matching. Through explicit exceptions, it allows to write code that will
+handle the possible edge cases that cannot be solved automatically in a
+way that does not interrupt execution, or requires manual input by the
+user. Given the breadth of the NCBI taxonomy database,
+\texttt{NCBITaxonomy.jl} is particularly suited to the name cleaning of
+large datasets of names.
+
 \textbf{Acknowledgements:} This work was supported by funding to the

### 2022-06-27 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_ncbitaxonomy_softwarenote@aa83c56a0a5fcc0340da9cffe96db0f5576f2c28 🚀

@@
 %
-\,\textsuperscript{3,4}\quad %
+\,\textsuperscript{3,4,5}\quad %
 \href{https://orcid.org/0000-0002-4308-6321}{Sadie J.\,Ryan}%
 %
-\,\textsuperscript{5,6,7}\quad %
+\,\textsuperscript{6,7,8}\quad %
 \href{https://orcid.org/0000-0001-6960-8434}{Colin J.\,Carlson}%
 %
-\,\textsuperscript{8,9}
+\,\textsuperscript{9,10}
 
@@
 Infectious Diseases, London School of Hygiene and Tropical Medicine,
-London, UK\quad \textsuperscript{5}\,Emerging Pathogens Institute,
+London, UK\quad \textsuperscript{5}\,Current address: Centre for
+Biodiversity and Environment Research, University College London,
+London, UK\quad \textsuperscript{6}\,Emerging Pathogens Institute,
 University of Florida, Gainesville, FL, United States of
-America\quad \textsuperscript{6}\,School of Life Sciences, University of
-KwaZulu-Natal, Durban, South Africa\quad \textsuperscript{7}\,Department
+America\quad \textsuperscript{7}\,School of Life Sciences, University of
+KwaZulu-Natal, Durban, South Africa\quad \textsuperscript{8}\,Department
 of Geography, University of Florida, Gainesville, FL, United States of
-America\quad \textsuperscript{8}\,Department of Microbiology and
+America\quad \textsuperscript{9}\,Department of Microbiology and
 Immunology, Georgetown University Medical Center, Georgetown University,
 Washington, D.C., United States of
-America\quad \textsuperscript{9}\,Center for Global Health Science and
+America\quad \textsuperscript{10}\,Center for Global Health Science and
 Security, Georgetown University Medical Center, Georgetown University,
@@
 These taxonomic changes have profound implications for the way we
-perceive biodiversity at global scales (Meier 2009), to the point were
-taxonomic revisions should sometimes be actively conducted to improve
-\emph{e.g.} conservation outcomes (Melville et al. 2021).
+perceive biodiversity at global scales (Dikow et al. 2009), to the point
+were taxonomic revisions should sometimes be actively conducted to
+improve \emph{e.g.} conservation outcomes (Melville et al. 2021).
 
@@
 
+\leavevmode\hypertarget{ref-Dikow2009BioRes}{}%
+Dikow, T. et al. 2009. Biodiversity Research Based on Taxonomic
+Revisions - A Tale of Unrealized Opportunities. - In: Diptera Diversity:
+Status, Challenges and Tools. Brill, pp. 323--346.
+
 \leavevmode\hypertarget{ref-Federhen2012NcbTax}{}%
@@
 Research 46: D708--D717.
-
-\leavevmode\hypertarget{ref-Meier2009BioRes}{}%
-Meier, R. 2009. Biodiversity Research Based on Taxonomic Revisions - A
-Tale of Unrealized Opportunities -. - In: pp. 323--345.
 

### 2022-06-27 preprint.tex
Deploying to gh-pages from @ PoisotLab/ms_ncbitaxonomy_softwarenote@aa83c56a0a5fcc0340da9cffe96db0f5576f2c28 🚀

@@
 %
-\,\textsuperscript{3,4}, %
+\,\textsuperscript{3,4,5}, %
 \href{https://orcid.org/0000-0002-4308-6321}{Sadie J.\,Ryan}%
 %
-\,\textsuperscript{5,6,7}, %
+\,\textsuperscript{6,7,8}, %
 \href{https://orcid.org/0000-0001-6960-8434}{Colin J.\,Carlson}%
 %
-\,\textsuperscript{8,9}
+\,\textsuperscript{9,10}
 \vskip 1em
@@
 Mathematical Modelling of Infectious Diseases, London School of Hygiene
-and Tropical Medicine, London, UK; \textsuperscript{5}\,Emerging
-Pathogens Institute, University of Florida, Gainesville, FL, United
-States of America; \textsuperscript{6}\,School of Life Sciences,
-University of KwaZulu-Natal, Durban, South
-Africa; \textsuperscript{7}\,Department of Geography, University of
-Florida, Gainesville, FL, United States of
-America; \textsuperscript{8}\,Department of Microbiology and Immunology,
+and Tropical Medicine, London, UK; \textsuperscript{5}\,Current address:
+Centre for Biodiversity and Environment Research, University College
+London, London, UK; \textsuperscript{6}\,Emerging Pathogens Institute,
+University of Florida, Gainesville, FL, United States of
+America; \textsuperscript{7}\,School of Life Sciences, University of
+KwaZulu-Natal, Durban, South Africa; \textsuperscript{8}\,Department of
+Geography, University of Florida, Gainesville, FL, United States of
+America; \textsuperscript{9}\,Department of Microbiology and Immunology,
 Georgetown University Medical Center, Georgetown University, Washington,
-D.C., United States of America; \textsuperscript{9}\,Center for Global
+D.C., United States of America; \textsuperscript{10}\,Center for Global
 Health Science and Security, Georgetown University Medical Center,

### 2023-01-24 Poisot_et_al_2023_ncbitaxonomyjl__draft.tex
Deploying to gh-pages from @ PoisotLab/ms_ncbitaxonomy_softwarenote@aabfcbf2552d76846f10d88446d3cdc8f18de681 🚀

--- 2022-06-27 draft.tex
@@
 \usepackage{lastpage}
+
+\usepackage{gensymb}
 
@@
 \setlength{\csllabelwidth}{3em}
-\newenvironment{CSLReferences}[3] % #1 hanging-ident, #2 entry spacing
+\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
  {% don't indent paragraphs
@@
 %
-\,\textsuperscript{9,10}
+\,\textsuperscript{10,9}
 
 \textsuperscript{1}\,Université de Montréal, Départment de Sciences
-Biologiques, Montréal QC, Canada\quad \textsuperscript{2}\,Québec Centre
-for Biodiversity Science, Montréal, QC,
-Canada\quad \textsuperscript{3}\,Centre on Climate Change and Planetary
-Health, London School of Hygiene and Tropical Medicine, London,
-UK\quad \textsuperscript{4}\,Centre for Mathematical Modelling of
-Infectious Diseases, London School of Hygiene and Tropical Medicine,
-London, UK\quad \textsuperscript{5}\,Current address: Centre for
-Biodiversity and Environment Research, University College London,
-London, UK\quad \textsuperscript{6}\,Emerging Pathogens Institute,
-University of Florida, Gainesville, FL, United States of
+Biologiques, Montréal QC, Canada\quad \textsuperscript{10}\,Center for
+Global Health Science and Security, Georgetown University Medical
+Center, Georgetown University, Washington, D.C., United States of
+America\quad \textsuperscript{2}\,Québec Centre for Biodiversity
+Science, Montréal, QC, Canada\quad \textsuperscript{3}\,Centre on
+Climate Change and Planetary Health, London School of Hygiene and
+Tropical Medicine, London, UK\quad \textsuperscript{4}\,Centre for
+Mathematical Modelling of Infectious Diseases, London School of Hygiene
+and Tropical Medicine, London, UK\quad \textsuperscript{5}\,Current
+address: Centre for Biodiversity and Environment Research, University
+College London, London, UK\quad \textsuperscript{6}\,Emerging Pathogens
+Institute, University of Florida, Gainesville, FL, United States of
 America\quad \textsuperscript{7}\,School of Life Sciences, University of
@@
 Immunology, Georgetown University Medical Center, Georgetown University,
-Washington, D.C., United States of
-America\quad \textsuperscript{10}\,Center for Global Health Science and
-Security, Georgetown University Medical Center, Georgetown University,
 Washington, D.C., United States of America
@@
 \vfill
-This work is released by its authors under a CC-BY 4.0 license\hfill\ccby\\
-Last revision: \emph{\today}
 
-\clearpage
-\thispagestyle{empty}
-
-\vfill
 \texttt{NCBITaxonomy.jl} is a package designed to facilitate the
@@
 \vfill
+This work is released by its authors under a CC-BY 4.0 license\hfill\ccby\\
+Last revision: \emph{\today}
+
+\clearpage
+\thispagestyle{empty}
+
+\vfill
+
+\vfill
 
@@
 may appear. There are a vast number of reasons for this. Different
-databases keep different taxonomic ``backbones,'' \emph{i.e.} different
+databases keep different taxonomic ``backbones'', \emph{i.e.} different
 data structures in which names are mapped to species, and organised in a
@@
 \begin{Highlighting}[]
-\ConstantTok{ENV}\NormalTok{[}\StringTok{"NCBITAXONOMY\_PATH"}\NormalTok{] }\OperatorTok{=}\NormalTok{ joinpath(homedir()}\OperatorTok{,} \StringTok{"data"}\OperatorTok{,} \StringTok{"NCBITaxonomy.jl"}\NormalTok{)}
+\ConstantTok{ENV}\NormalTok{[}\StringTok{"NCBITAXONOMY\_PATH"}\NormalTok{] }\OperatorTok{=} \FunctionTok{joinpath}\NormalTok{(}\FunctionTok{homedir}\NormalTok{(), }\StringTok{"data"}\NormalTok{, }\StringTok{"NCBITaxonomy.jl"}\NormalTok{)}
 \end{Highlighting}
@@
 \begin{Highlighting}[]
-\KeywordTok{using}\NormalTok{ Pkg}
-\NormalTok{Pkg.add(}\StringTok{"NCBITaxonomy"}\NormalTok{) }\CommentTok{\# Dowloading the files may take a long time}
+\ImportTok{using} \BuiltInTok{Pkg}
+\BuiltInTok{Pkg}\NormalTok{.}\FunctionTok{add}\NormalTok{(}\StringTok{"NCBITaxonomy"}\NormalTok{) }\CommentTok{\# Dowloading the files may take a long time}
 \end{Highlighting}
@@
 \begin{Highlighting}[]
-\NormalTok{julia}\OperatorTok{\textgreater{}}\NormalTok{ similarnames(}\StringTok{"Adeno{-}associated virus 3b"}\OperatorTok{;}\NormalTok{ threshold}\OperatorTok{=}\FloatTok{0.95}\NormalTok{)}
-\FloatTok{3}\OperatorTok{{-}}\NormalTok{element }\DataTypeTok{Vector}\NormalTok{\{}\DataTypeTok{Pair}\NormalTok{\{NCBITaxon}\OperatorTok{,} \DataTypeTok{Float64}\NormalTok{\}\}}\OperatorTok{:}
+\NormalTok{julia}\OperatorTok{\textgreater{}} \FunctionTok{similarnames}\NormalTok{(}\StringTok{"Adeno{-}associated virus 3b"}\NormalTok{; threshold}\OperatorTok{=}\FloatTok{0.95}\NormalTok{)}
+\FloatTok{3}\OperatorTok{{-}}\NormalTok{element }\DataTypeTok{Vector}\NormalTok{\{}\DataTypeTok{Pair}\NormalTok{\{NCBITaxon, }\DataTypeTok{Float64}\NormalTok{\}\}}\OperatorTok{:}
 \NormalTok{  Adeno}\OperatorTok{{-}}\NormalTok{associated virus }\OperatorTok{{-}} \FloatTok{3}\NormalTok{ (ncbi}\OperatorTok{:}\FloatTok{46350}\NormalTok{) }\OperatorTok{=\textgreater{}} \FloatTok{0.96}
@@
 \begin{Highlighting}[]
-\NormalTok{julia}\OperatorTok{\textgreater{}}\NormalTok{ taxon(}\StringTok{"Adeno{-}associated virus 3b"}\OperatorTok{;}\NormalTok{ casesensitive}\OperatorTok{=}\ExtensionTok{false}\NormalTok{)}
+\NormalTok{julia}\OperatorTok{\textgreater{}} \FunctionTok{taxon}\NormalTok{(}\StringTok{"Adeno{-}associated virus 3b"}\NormalTok{; casesensitive}\OperatorTok{=}\ConstantTok{false}\NormalTok{)}
 \NormalTok{Adeno}\OperatorTok{{-}}\NormalTok{associated virus }\FloatTok{3}\NormalTok{B (ncbi}\OperatorTok{:}\FloatTok{68742}\NormalTok{)}
@@
 \begin{Highlighting}[]
-\KeywordTok{try}
-\NormalTok{  taxon(name)}
+\NormalTok{try}
+  \FunctionTok{taxon}\NormalTok{(name)}
   \CommentTok{\# Additional operations with the matched name}
-\KeywordTok{catch}\NormalTok{ err}
-  \KeywordTok{if}\NormalTok{ isa(err}\OperatorTok{,}\NormalTok{ NameHasNoDirectMatch)}
+\NormalTok{catch err}
+  \ControlFlowTok{if} \FunctionTok{isa}\NormalTok{(err, NameHasNoDirectMatch)}
     \CommentTok{\# What to do if no match is found}
-  \KeywordTok{elseif}\NormalTok{ isa(err}\OperatorTok{,}\NormalTok{ NameHasMultipleMatches)}
+  \ControlFlowTok{elseif} \FunctionTok{isa}\NormalTok{(err, NameHasMultipleMatches)}
     \CommentTok{\# What to do if there are multiple matches}
-  \KeywordTok{else}
+  \ControlFlowTok{else}
     \CommentTok{\# What to do in case of another error that is not NCBITaxonomy specific}
-  \KeywordTok{end}
+  \ControlFlowTok{end}
 \KeywordTok{end}
@@
 
-\begin{longtable}[]{@{}lclll@{}}
-\toprule
-Names list & Fuzzy matching & Time (ms) & Allocations & Memory
-allocated\tabularnewline
-\midrule
+\begin{longtable}[]{@{}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.2857}}
+  >{\centering\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.2000}}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.1286}}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.1571}}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.2286}}@{}}
+\toprule()
+\begin{minipage}[b]{\linewidth}\raggedright
+Names list
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+Fuzzy matching
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
+Time (ms)
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
+Allocations
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
+Memory allocated
+\end{minipage} \\
+\midrule()
 \endhead
-all & no & 23 & 34 & 2 KiB\tabularnewline
-& yes & 105 & 2580 & 25 MiB\tabularnewline
-\texttt{mammalfilter(true)} & no & 0.55 & 32 & 2 KiB\tabularnewline
-& yes & 1.9 & 551 & 286 KiB\tabularnewline
-\texttt{primatefilter()} & no & 0.15 & 33 & 2 KiB\tabularnewline
-& yes & 0.3 & 92 & 27 KiB\tabularnewline
-\bottomrule
+all & no & 23 & 34 & 2 KiB \\
+& yes & 105 & 2580 & 25 MiB \\
+\texttt{mammalfilter(true)} & no & 0.55 & 32 & 2 KiB \\
+& yes & 1.9 & 551 & 286 KiB \\
+\texttt{primatefilter()} & no & 0.15 & 33 & 2 KiB \\
+& yes & 0.3 & 92 & 27 KiB \\
+\bottomrule()
 \end{longtable}
@@
 \begin{CSLReferences}{1}{0}
-\leavevmode\hypertarget{ref-Barchard2011PreHum}{}%
-Barchard, K. and Pace, L. 2011. Preventing human error: The impact of
-data entry methods on data accuracy and statistical results. - Computers
-in Human Behavior 27: 1834--1839.
+\leavevmode\vadjust pre{\hypertarget{ref-Barchard2011PreHum}{}}%
+Barchard, K. and Pace, L. 2011.
+\href{https://doi.org/10.1016/j.chb.2011.04.004}{Preventing human error:
+The impact of data entry methods on data accuracy and statistical
+results}. - Computers in Human Behavior 27: 1834--1839.
 
-\leavevmode\hypertarget{ref-Bezanson2017JulFre}{}%
-Bezanson, J. et al. 2017. Julia: A Fresh Approach to Numerical
-Computing. - SIAM Review 59: 65--98.
+\leavevmode\vadjust pre{\hypertarget{ref-Bezanson2017JulFre}{}}%
+Bezanson, J. et al. 2017.
+\href{https://doi.org/10.1137/141000671}{Julia: A Fresh Approach to
+Numerical Computing}. - SIAM Review 59: 65--98.
 
-\leavevmode\hypertarget{ref-Carlson2022GloVir}{}%
-Carlson, C. J. et al. 2022. The Global Virome in One Network (VIRION):
-An Atlas of Vertebrate-Virus Associations. - mBio in press.
+\leavevmode\vadjust pre{\hypertarget{ref-Carlson2022GloVir}{}}%
+Carlson, C. J. et al. 2022.
+\href{https://doi.org/10.1128/mbio.02985-21}{The Global Virome in One
+Network (VIRION): An Atlas of Vertebrate-Virus Associations}. - mBio in
+press.
 
-\leavevmode\hypertarget{ref-Chamberlain2013TaxTax}{}%
-Chamberlain, S. A. and Szöcs, E. 2013. Taxize: Taxonomic search and
-retrieval in R. - F1000Research 2: 191.
+\leavevmode\vadjust pre{\hypertarget{ref-Chamberlain2013TaxTax}{}}%
+Chamberlain, S. A. and Szöcs, E. 2013.
+\href{https://doi.org/10.12688/f1000research.2-191.v2}{Taxize: Taxonomic
+search and retrieval in R}. - F1000Research 2: 191.
 
-\leavevmode\hypertarget{ref-Conti2021MatAlg}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-Conti2021MatAlg}{}}%
 Conti, M. et al. 2021. Match Algorithms for Scientific Names in
@@
 
-\leavevmode\hypertarget{ref-Dauncey2016ComMis}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-Dauncey2016ComMis}{}}%
 Dauncey, E. A. et al. 2016. Common mistakes when using plant names and
@@
 
-\leavevmode\hypertarget{ref-Dikow2009BioRes}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-Dikow2009BioRes}{}}%
 Dikow, T. et al. 2009. Biodiversity Research Based on Taxonomic
@@
 
-\leavevmode\hypertarget{ref-Federhen2012NcbTax}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-Federhen2012NcbTax}{}}%
 Federhen, S. 2012. The NCBI taxonomy database. - Nucleic acids research
@@
 
-\leavevmode\hypertarget{ref-Gibb2021DatPro}{}%
-Gibb, R. et al. 2021. Data Proliferation, Reconciliation, and Synthesis
-in Viral Ecology. - BioScience in press.
+\leavevmode\vadjust pre{\hypertarget{ref-Gibb2021DatPro}{}}%
+Gibb, R. et al. 2021. \href{https://doi.org/10.1093/biosci/biab080}{Data
+Proliferation, Reconciliation, and Synthesis in Viral Ecology}. -
+BioScience in press.
 
-\leavevmode\hypertarget{ref-Lefkowitz2018VirTax}{}%
-Lefkowitz, E. J. et al. 2018. Virus taxonomy: The database of the
-International Committee on Taxonomy of Viruses (ICTV). - Nucleic Acids
-Research 46: D708--D717.
+\leavevmode\vadjust pre{\hypertarget{ref-Lefkowitz2018VirTax}{}}%
+Lefkowitz, E. J. et al. 2018.
+\href{https://doi.org/10.1093/nar/gkx932}{Virus taxonomy: The database
+of the International Committee on Taxonomy of Viruses (ICTV)}. - Nucleic
+Acids Research 46: D708--D717.
 
-\leavevmode\hypertarget{ref-Melville2021RetApp}{}%
-Melville, J. et al. 2021. A return-on-investment approach for
-prioritization of rigorous taxonomic research needed to inform responses
-to the biodiversity crisis. - PLOS Biology 19: e3001210.
+\leavevmode\vadjust pre{\hypertarget{ref-Melville2021RetApp}{}}%
+Melville, J. et al. 2021.
+\href{https://doi.org/10.1371/journal.pbio.3001210}{A
+return-on-investment approach for prioritization of rigorous taxonomic
+research needed to inform responses to the biodiversity crisis}. - PLOS
+Biology 19: e3001210.
 
-\leavevmode\hypertarget{ref-Norman2020TaxHig}{}%
-Norman, K. E. A. et al. 2020. Taxadb: A high-performance local taxonomic
-database interface. - Methods in Ecology and Evolution 11: 1153--1159.
+\leavevmode\vadjust pre{\hypertarget{ref-Norman2020TaxHig}{}}%
+Norman, K. E. A. et al. 2020.
+\href{https://doi.org/10.1111/2041-210X.13440}{Taxadb: A
+high-performance local taxonomic database interface}. - Methods in
+Ecology and Evolution 11: 1153--1159.
 
-\leavevmode\hypertarget{ref-Schoch2020NcbTax}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-Schoch2020NcbTax}{}}%
 Schoch, C. L. et al. 2020. NCBI Taxonomy: A comprehensive update on
@@
 
-\leavevmode\hypertarget{ref-Shimatani2001MeaSpe}{}%
-Shimatani, K. 2001. On the Measurement of Species Diversity
-Incorporating Species Differences. - Oikos 93: 135--147.
+\leavevmode\vadjust pre{\hypertarget{ref-Shimatani2001MeaSpe}{}}%
+Shimatani, K. 2001. \href{https://www.jstor.org/stable/3547217}{On the
+Measurement of Species Diversity Incorporating Species Differences}. -
+Oikos 93: 135--147.
 
-\leavevmode\hypertarget{ref-Wagner2016RevSof}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-Wagner2016RevSof}{}}%
 Wagner, V. 2016. A review of software tools for spell-checking taxon
@@
 
-\leavevmode\hypertarget{ref-Walker2020ChaVir}{}%
-Walker, P. J. et al. 2020. Changes to virus taxonomy and the Statutes
-ratified by the International Committee on Taxonomy of Viruses (2020). -
-Archives of Virology 165: 2737--2748.
+\leavevmode\vadjust pre{\hypertarget{ref-Walker2020ChaVir}{}}%
+Walker, P. J. et al. 2020.
+\href{https://doi.org/10.1007/s00705-020-04752-x}{Changes to virus
+taxonomy and the Statutes ratified by the International Committee on
+Taxonomy of Viruses (2020)}. - Archives of Virology 165: 2737--2748.
 

### 2023-01-24 Poisot_et_al_2023_ncbitaxonomyjl__preprint.tex
Deploying to gh-pages from @ PoisotLab/ms_ncbitaxonomy_softwarenote@aabfcbf2552d76846f10d88446d3cdc8f18de681 🚀

--- 2023-01-24 Poisot_et_al_2023_ncbitaxonomyjl__draft.tex
@@
 }
+
+\usepackage{tikz}
 \begin{document}
-\raggedright
-\thispagestyle{empty}
-{\Large\bfseries\sffamily NCBITaxonomy.jl - rapid biological names
-finding and reconciliation}
-\vskip 5em
+\tikz [remember picture, overlay] %
+\node [shift={(-0.6in,1.1cm)},scale=0.2,opacity=0.4] at (current page.south east)[anchor=south east]{\includegraphics{logo}};%
+\pagestyle{normal}
+\thispagestyle{firstpage}
 
+\newcommand{\colorRule}[3][black]{\textcolor[HTML]{#1}{\rule{#2}{#3}}}
+
+\noindent {\LARGE \textbf{\textsf{NCBITaxonomy.jl - rapid biological
+names finding and reconciliation}}}
+
+\medskip
+\begin{flushleft}
+{\small
 %
@@
 %
-\,\textsuperscript{1,2}\quad %
+\,\textsuperscript{1,2}, %
 \href{https://orcid.org/0000-0002-0965-1649}{Rory\,Gibb}%
 %
-\,\textsuperscript{3,4,5}\quad %
+\,\textsuperscript{3,4,5}, %
 \href{https://orcid.org/0000-0002-4308-6321}{Sadie J.\,Ryan}%
 %
-\,\textsuperscript{6,7,8}\quad %
+\,\textsuperscript{6,7,8}, %
 \href{https://orcid.org/0000-0001-6960-8434}{Colin J.\,Carlson}%
@@
 \,\textsuperscript{10,9}
-
+\vskip 1em
 \textsuperscript{1}\,Université de Montréal, Départment de Sciences
-Biologiques, Montréal QC, Canada\quad \textsuperscript{10}\,Center for
+Biologiques, Montréal QC, Canada; \textsuperscript{10}\,Center for
 Global Health Science and Security, Georgetown University Medical
 Center, Georgetown University, Washington, D.C., United States of
-America\quad \textsuperscript{2}\,Québec Centre for Biodiversity
-Science, Montréal, QC, Canada\quad \textsuperscript{3}\,Centre on
-Climate Change and Planetary Health, London School of Hygiene and
-Tropical Medicine, London, UK\quad \textsuperscript{4}\,Centre for
-Mathematical Modelling of Infectious Diseases, London School of Hygiene
-and Tropical Medicine, London, UK\quad \textsuperscript{5}\,Current
-address: Centre for Biodiversity and Environment Research, University
-College London, London, UK\quad \textsuperscript{6}\,Emerging Pathogens
-Institute, University of Florida, Gainesville, FL, United States of
-America\quad \textsuperscript{7}\,School of Life Sciences, University of
-KwaZulu-Natal, Durban, South Africa\quad \textsuperscript{8}\,Department
-of Geography, University of Florida, Gainesville, FL, United States of
-America\quad \textsuperscript{9}\,Department of Microbiology and
-Immunology, Georgetown University Medical Center, Georgetown University,
-Washington, D.C., United States of America
-
+America; \textsuperscript{2}\,Québec Centre for Biodiversity Science,
+Montréal, QC, Canada; \textsuperscript{3}\,Centre on Climate Change and
+Planetary Health, London School of Hygiene and Tropical Medicine,
+London, UK; \textsuperscript{4}\,Centre for Mathematical Modelling of
+Infectious Diseases, London School of Hygiene and Tropical Medicine,
+London, UK; \textsuperscript{5}\,Current address: Centre for
+Biodiversity and Environment Research, University College London,
+London, UK; \textsuperscript{6}\,Emerging Pathogens Institute,
+University of Florida, Gainesville, FL, United States of
+America; \textsuperscript{7}\,School of Life Sciences, University of
+KwaZulu-Natal, Durban, South Africa; \textsuperscript{8}\,Department of
+Geography, University of Florida, Gainesville, FL, United States of
+America; \textsuperscript{9}\,Department of Microbiology and Immunology,
+Georgetown University Medical Center, Georgetown University, Washington,
+D.C., United States of America\\
+\vskip 1em
 \textbf{Correspondance to:}\\
 Timothée Poisot --- \texttt{timothee.poisot@umontreal.ca}\\
+}
+\end{flushleft}
 
-\vfill
+\vskip 2em
+\makebox[0pt][l]{\colorRule[CCCCCC]{2.0\textwidth}{0.5pt}}
+\vskip 2em
+\noindent
+
+\marginpar{\vskip 1em\flushright
+{\small{\bfseries Keywords}:\par
+biodiversity\\taxonomy\\NCBI\\fuzzy matching\\}
+}
 
@@
 
-\vfill
-This work is released by its authors under a CC-BY 4.0 license\hfill\ccby\\
-Last revision: \emph{\today}
-
-\clearpage
-\thispagestyle{empty}
-
-\vfill
-
-\vfill
-
-\clearpage
-\linenumbers
-\pagestyle{normal}
+\vskip 2em
+\makebox[0pt][l]{\colorRule[CCCCCC]{2.0\textwidth}{0.5pt}}
+\vskip 2em
 

### 2023-01-24 Poisot_et_al_2023_ncbitaxonomyjl__draft.tex
Deploying to gh-pages from @ PoisotLab/ms_ncbitaxonomy_softwarenote@08ded612bd8bda0c46eddd995b9850c9683d8208 🚀

@@
 Viral Emergence Research Initiative (VERENA) consortium including NSF
-BII 2021909 and a grant from Institut de Valorisation des Données
-(IVADO), by the NSERC Discovery Grants and Discovery Acceleration
-Supplement programs, and by a donation from the Courtois Foundation.
-Benchmarking of this package on distributed systems was enabled by
-support provided by Calcul Québec (\texttt{www.calculquebec.ca}) and
-Compute Canada (\texttt{www.computecanada.ca}). TP wrote the initial
-code, TP and CJC contributed to API design, and all authors contributed
-to functionalities and usability testing.
+BII 2021909 and 2213854 and a grant from Institut de Valorisation des
+Données (IVADO), by the NSERC Discovery Grants and Discovery
+Acceleration Supplement programs, and by a donation from the Courtois
+Foundation. Benchmarking of this package on distributed systems was
+enabled by support provided by Calcul Québec
+(\texttt{www.calculquebec.ca}) and Compute Canada
+(\texttt{www.computecanada.ca}). TP wrote the initial code, TP and CJC
+contributed to API design, and all authors contributed to
+functionalities and usability testing.
 

### 2023-01-24 Poisot_et_al_2023_ncbitaxonomyjl__draft.tex
Deploying to gh-pages from @ PoisotLab/ms_ncbitaxonomy_softwarenote@5b8bfd89b09323b98fb36465b3c4d98c36fa1b45 🚀

@@
 An up-to-date version of the documentation for \texttt{NCBITaxonomy.jl}
-can be found online from the EcoJulia documentation hub
-\href{https://docs.ecojulia.org/NCBITaxonomy.jl/stable/}{https://docs.ecojulia.org/},
-including examples and in-line documentation of every method. The
-package is released under the MIT license. Contributions can be made in
-the form of issues (bug reports, questions, features suggestions) and
-pull requests.
+can be found in the package \texttt{git} repository
+(\url{https://github.com/PoisotLab/NCBITaxonomy.jl}), including examples
+and in-line documentation of every method. The package is released under
+the MIT license. Contributions can be made in the form of issues (bug
+reports, questions, features suggestions) and pull requests.
 
@@
 it locally, and pre-process it as a set of Julia data tables. By
-default, the taxonomy will be downloaded to the Julia package
-repository, which is not an ideal solution, and therefore we recommend
-that users set an environment variable to specificy where the data will
-be loaded from (this path will be created if it doesn't exist):
+default, the taxonomy will be downloaded to the user's hoome directory,
+which is not an ideal solution, and therefore we recommend that users
+set an environment variable to specificy where the data will be loaded
+from (this path will be created if it doesn't exist):
 
@@
 Note that this location can be different for different projects, as the
-package is able to update the taxoonmic backbone (and will indeed prompt
+package is able to update the taxonomic backbone (and will indeed prompt
 the user to do so if the taxonomy is more than 90 days old). The package
@@
 
-This software note describes version \texttt{v0.2.3} of the package (we
+This software note describes version \texttt{v0.3.0} of the package (we
 follow semantic versioning), which works on Julia 1.5 upwards. The
